How does increasing $s$ and $k$ effect log normalising constant estimation

### 2023-04-11 src/naomi-simple_increase-s-k/increase-s-k.Rmd
Add k = 3 to plot #22

```{r}
lognormconsts <- c(
  s1k2$normalized_posterior$lognormconst,
  s2k2$normalized_posterior$lognormconst,
  s3k2$normalized_posterior$lognormconst,
  s4k2$normalized_posterior$lognormconst,
  s5k2$normalized_posterior$lognormconst
)

df <- data.frame(
  s = 1:5,
  k = 2,
  lognormconst = lognormconsts
)

@@

```{r}
ggplot(df, aes(x = s, y = lognormconst)) +
  geom_point() +
  facet_grid(k ~ .) +
  labs(x = "Dimensions kept of the PCA", y = "Log normalising constant") +
  theme_minimal()
```

>>>>

```{r}
k2 <- list(s1k2, s2k2, s3k2, s4k2, s5k2)
k3 <- list(s1k3, s2k3, s3k3, s4k2, s5k3)

df <- data.frame(
  s = rep(1:5, times = 2),
  k = rep(2:3, each = 5),
  lognormconst = sapply(c(k2, k2), function(x) x$normalized_posterior$lognormconst)
)

@@

```{r}
ggplot(df, aes(x = s, y = lognormconst)) +
  geom_point() +
  facet_grid(. ~ k) +
  labs(x = "Dimensions kept of the PCA", y = "Log normalising constant") +
  theme_minimal()
```
